The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
reflow
spacetime cap edits

(ref:spacetime) Space-time diagram displaying variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including hyaena, passerine birds, sleepy lizards, and elephants. Spatial and temporal extent for social interactions, e.g. mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for most social interactions. The logical extension is that spatial and temporal extent for social interaction is nested within the spatial and temporal extent for social association because individuals must shared space to interact. By contrast, different species have potential for  greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.

>>>>

(ref:spacetime) Space-time diagram displaying variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including hyaena, passerine birds, sleepy lizards, and elephants. Spatial and temporal extent for social interactions, e.g. mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for most social interactions. The logical extension is that spatial and temporal extent for social interaction is hierarchically nested within the spatial and temporal extent for social association because individuals must shared space to interact. By contrast, different species have potential for  greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.
